---
title: "StreamCurves — Geomorphic Reference Curve Analysis"
subtitle: "Technical Appendix"
format:
  pdf:
    documentclass: article
    papersize: letter
    geometry:
      - margin=1in
    toc: true
    toc-depth: 3
    number-sections: true
    keep-tex: false
    fig-width: 7
    fig-height: 5
params:
  run_dir: "../outputs/run_latest"
---

```{r setup, include=FALSE}
library(tidyverse)
library(gt)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center")

run_dir <- params$run_dir
if (!dir.exists(run_dir)) {
  all_runs <- list.dirs("../outputs", recursive = FALSE, full.names = TRUE)
  all_runs <- sort(all_runs, decreasing = TRUE)
  if (length(all_runs) > 0) run_dir <- all_runs[1]
}

tables_dir <- file.path(run_dir, "tables")
plots_dir  <- file.path(run_dir, "plots")

safe_read <- function(path) {
  if (file.exists(path)) readr::read_csv(path, show_col_types = FALSE)
  else tibble::tibble()
}
```

# Introduction

This appendix provides the complete technical analysis for all StreamCurves geomorphic reference-curve metrics. Each metric section includes data quality checks, stratification screening, model selection, diagnostics, and reference curve development.

# Data Quality

## Metric Precheck

```{r precheck}
precheck <- safe_read(file.path(tables_dir, "metric_precheck.csv"))
if (nrow(precheck) > 0) {
  gt::gt(precheck |> select(metric, display_name, n_obs, n_missing, min, median, max, sd, precheck_status)) |>
    gt::fmt_number(columns = c(min, median, max, sd), decimals = 2) |>
    gt::tab_header(title = "Metric Data Quality Summary")
}
```

# Stratification Analysis

## Screening Results

```{r strat-screening}
strat_results <- safe_read(file.path(tables_dir, "stratification_screening.csv"))
if (nrow(strat_results) > 0) {
  gt::gt(strat_results |>
    select(metric, stratification, test, statistic, p_value, n_groups, min_group_n, classification) |>
    mutate(p_value = round(p_value, 4), statistic = round(statistic, 2))
  ) |>
    gt::tab_header(title = "Stratification Screening Results")
}
```

## Decisions

```{r strat-decisions}
strat_dec <- safe_read(file.path(tables_dir, "stratification_decisions.csv"))
if (nrow(strat_dec) > 0) {
  gt::gt(strat_dec) |>
    gt::fmt_number(columns = where(is.numeric), decimals = 4) |>
    gt::tab_header(title = "Stratification Decisions")
}
```

# Per-Metric Analysis

```{r per-metric, results='asis', fig.width=7, fig.height=5}
model_sel <- safe_read(file.path(tables_dir, "model_selections.csv"))
model_cands <- safe_read(file.path(tables_dir, "model_candidates.csv"))
diag_summary <- safe_read(file.path(tables_dir, "diagnostic_summary.csv"))
ref_curves <- safe_read(file.path(tables_dir, "reference_curves.csv"))

if (nrow(model_sel) > 0) {
  for (i in seq_len(nrow(model_sel))) {
    mk <- model_sel$metric[i]
    cat("\n\n## ", mk, "\n\n")

    # Model selection
    sel <- model_sel |> filter(metric == mk)
    cat("**Selected model:** ", sel$predictors, "\n\n")
    cat("**Adj R²:** ", round(sel$adj_r2, 3), " | **BIC:** ", round(sel$bic, 1),
        " | **Top models:** ", sel$n_top_models, "\n\n")

    # Diagnostics
    diag <- diag_summary |> filter(metric == mk)
    if (nrow(diag) > 0) {
      cat("**Diagnostics:** ", diag$overall_status,
          " (Shapiro p=", round(diag$shapiro_p, 4),
          ", BP p=", round(diag$bp_p, 4),
          ", Max VIF=", round(diag$max_vif, 2), ")\n\n")
    }

    # Reference curve
    rc <- ref_curves |> filter(metric == mk)
    if (nrow(rc) > 0) {
      cat("**Reference IQR:** [", round(rc$q25, 1), ", ", round(rc$q75, 1), "]\n\n")
    }

    # Include diagnostic plot if exists
    diag_plot <- file.path(plots_dir, paste0(mk, "_diagnostic_4panel.png"))
    if (file.exists(diag_plot)) {
      cat("![", mk, " Diagnostics](", diag_plot, ")\n\n")
    }

    # Include reference bar chart if exists
    bar_plot <- file.path(plots_dir, paste0(mk, "_reference_bar_chart.png"))
    if (file.exists(bar_plot)) {
      cat("![", mk, " Reference Bar Chart](", bar_plot, ")\n\n")
    }

    # Include reference curve plot if exists
    ref_plot <- file.path(plots_dir, paste0(mk, "_reference_curve.png"))
    if (file.exists(ref_plot)) {
      cat("![", mk, " Reference Curve](", ref_plot, ")\n\n")
    }

    cat("\\newpage\n\n")
  }
}
```

# Cross-Metric Analysis

## Correlation Analysis

```{r cross-metric}
redundancy <- safe_read(file.path(tables_dir, "metric_redundancy_results.csv"))
if (nrow(redundancy) > 0) {
  gt::gt(redundancy |>
    filter(abs_pearson > 0.5) |>
    arrange(desc(abs_pearson)) |>
    select(display_1, display_2, pearson_r, spearman_rho, redundant_flag)
  ) |>
    gt::fmt_number(columns = c(pearson_r, spearman_rho), decimals = 3) |>
    gt::tab_header(title = "Metric Pairs with |r| > 0.50")
}

# Include correlation heatmap
heatmap_path <- file.path(plots_dir, "correlation_heatmap.png")
if (file.exists(heatmap_path)) {
  knitr::include_graphics(heatmap_path)
}
```

# Regional Curves

```{r regional}
regional <- safe_read(file.path(tables_dir, "regional_curves_results.csv"))
if (nrow(regional) > 0) {
  gt::gt(regional |>
    select(response, predictor, group_var, group_level, n_obs,
           coefficient_a, exponent_b, r_squared, fit_status)
  ) |>
    gt::fmt_number(columns = c(coefficient_a, exponent_b, r_squared), decimals = 3) |>
    gt::tab_header(title = "Regional Hydraulic Geometry Curves")
}
```

# QA Summary

```{r qa}
qa_log <- safe_read(file.path(run_dir, "logs", "qa_log.csv"))
if (nrow(qa_log) > 0) {
  gt::gt(qa_log) |> gt::tab_header(title = "QA Log")
}

pipeline_log <- safe_read(file.path(run_dir, "logs", "pipeline_log.csv"))
if (nrow(pipeline_log) > 0) {
  gt::gt(pipeline_log) |> gt::tab_header(title = "Pipeline Execution Log")
}
```

# Session Information

```{r session-info}
session_path <- file.path(run_dir, "manifest", "session_info.txt")
if (file.exists(session_path)) {
  cat(readLines(session_path), sep = "\n")
}
```
