---
title: "StreamCurves — Geomorphic Reference Curve Summary"
subtitle: "Condensed Analysis Results"
format:
  pdf:
    documentclass: article
    papersize: letter
    geometry:
      - margin=0.75in
      - landscape
    keep-tex: false
    fig-width: 9
    fig-height: 5
params:
  run_dir: "../outputs/run_latest"
---

```{r setup, include=FALSE}
library(tidyverse)
library(gt)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

run_dir <- params$run_dir
if (!dir.exists(run_dir)) {
  all_runs <- list.dirs("../outputs", recursive = FALSE, full.names = TRUE)
  all_runs <- sort(all_runs, decreasing = TRUE)
  if (length(all_runs) > 0) run_dir <- all_runs[1]
}

tables_dir <- file.path(run_dir, "tables")
safe_read <- function(path) {
  if (file.exists(path)) readr::read_csv(path, show_col_types = FALSE)
  else tibble::tibble()
}
```

# Analysis Overview

This report summarizes the geomorphic reference-curve analysis across three ecoregions (Region_A, Region_B, Region_C). The analysis covers `r nrow(safe_read(file.path(tables_dir, "metric_precheck.csv")))` stream metrics using the loaded dataset.

## Key Results

```{r summary-table}
model_sel <- safe_read(file.path(tables_dir, "model_selections.csv"))
diag_summary <- safe_read(file.path(tables_dir, "diagnostic_summary.csv"))
ref_curves <- safe_read(file.path(tables_dir, "reference_curves.csv"))
strat_dec <- safe_read(file.path(tables_dir, "stratification_decisions.csv"))

if (nrow(model_sel) > 0) {
  summary <- model_sel |>
    left_join(strat_dec |> select(metric, selected_strat), by = "metric") |>
    left_join(diag_summary |> select(metric, overall_status), by = "metric") |>
    left_join(ref_curves |> select(metric, display_name, q25, q75), by = "metric") |>
    select(display_name, selected_strat, predictors, adj_r2,
           overall_status, q25, q75, needs_review) |>
    rename(
      Metric = display_name,
      Stratification = selected_strat,
      Predictors = predictors,
      `Adj R²` = adj_r2,
      Diagnostics = overall_status,
      Q25 = q25,
      Q75 = q75,
      Review = needs_review
    )

  gt::gt(summary) |>
    gt::fmt_number(columns = c(`Adj R²`), decimals = 3) |>
    gt::fmt_number(columns = c(Q25, Q75), decimals = 1) |>
    gt::tab_header(title = "Metric Analysis Summary") |>
    gt::tab_footnote("IQR (Q25-Q75) defines the Functioning range (score 0.70-1.00)")
}
```

## Scoring Categories

| Category | Score Range | Description |
|----------|-----------|-------------|
| Functioning | 0.70 - 1.00 | Within IQR of reference-standard sites |
| Functioning-at-Risk | 0.30 - 0.69 | Below/above reference IQR |
| Not Functioning | 0.00 - 0.29 | Well outside reference range |

## Diagnostics Summary

```{r diagnostics-summary}
if (nrow(diag_summary) > 0) {
  cat("Pass:", sum(diag_summary$overall_status == "pass", na.rm = TRUE), "\n")
  cat("Caution:", sum(diag_summary$overall_status == "caution", na.rm = TRUE), "\n")
  cat("Fail:", sum(diag_summary$overall_status == "fail", na.rm = TRUE), "\n")
}
```

## Metrics Requiring Review

```{r review-flags}
if (nrow(model_sel) > 0) {
  review_items <- model_sel |> filter(needs_review == TRUE)
  if (nrow(review_items) > 0) {
    gt::gt(review_items |> select(metric, predictors, review_reason)) |>
      gt::tab_header(title = "Metrics Flagged for Review")
  } else {
    cat("No metrics flagged for review.")
  }
}
```
