---
title: "StreamCurves - Export Summary"
subtitle: "Current Session Snapshot"
format:
  pdf:
    documentclass: article
    papersize: letter
    geometry:
      - margin=0.75in
    keep-tex: false
params:
  session_dir: null
---

```{r setup, include=FALSE}
library(dplyr)
library(gt)
library(tibble)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

`%||%` <- function(x, y) {
  if (is.null(x)) y else x
}

if (is.null(params$session_dir) || !dir.exists(params$session_dir)) {
  stop("A valid session_dir parameter is required.")
}

session_dir <- normalizePath(params$session_dir, winslash = "/", mustWork = TRUE)
context_path <- file.path(session_dir, "report_context.rds")
if (!file.exists(context_path)) {
  stop("report_context.rds was not found in session_dir.")
}

ctx <- readRDS(context_path)
session_meta <- ctx$session_meta %||% list()
metric_status <- tibble::as_tibble(ctx$metric_status %||% tibble())
regional_curves <- tibble::as_tibble(ctx$regional_curves %||% tibble())
```

# Session Overview

- Generated: `r session_meta$generated_at %||% "Unknown"`
- Summary metrics: `r session_meta$metric_count %||% 0`
- Curves ready: `r session_meta$complete_metrics %||% 0`
- Pending metrics: `r session_meta$pending_metrics %||% 0`
- Metrics needing review: `r session_meta$review_metrics %||% 0`
- Manual curve metrics: `r session_meta$manual_curve_metrics %||% 0`
- Regional curve sets: `r session_meta$regional_curve_sets %||% 0`

# Priority Review Items

```{r review-items}
review_items <- metric_status |>
  filter((needs_review %in% TRUE) | status_label == "Incomplete") |>
  select(
    Metric = display_name,
    Status = status_label,
    `Selected Stratification` = selected_curve_stratification_label,
    `Recommended Stratification` = recommended_curve_stratification_label,
    `Manual Curve` = manual_curve_label,
    Warnings = warning_summary
  )

if (nrow(review_items) == 0) {
  cat("No metrics currently require review.")
} else {
  gt(review_items) |>
    fmt_missing(columns = everything(), missing_text = "-") |>
    tab_header(title = "Metrics Requiring Attention")
}
```

# Current Metric Status

```{r metric-status}
status_tbl <- metric_status |>
  select(
    Metric = display_name,
    Status = status_label,
    `Selected Stratification` = selected_curve_stratification_label,
    `Recommended Stratification` = recommended_curve_stratification_label,
    `Curve Summary` = curve_summary,
    `Manual Curve` = manual_curve_label
  )

if (nrow(status_tbl) == 0) {
  cat("No summary metrics are available in the current session.")
} else {
  gt(status_tbl) |>
    fmt_missing(columns = everything(), missing_text = "-") |>
    tab_header(title = "Current Summary-Metric State")
}
```

# Regional Outputs

```{r regional-summary}
if (nrow(regional_curves) == 0) {
  cat("No regional curve outputs are available in the current session.")
} else {
  regional_tbl <- regional_curves |>
    select(
      Response = response,
      Predictor = predictor,
      Stratification = stratify,
      `Fit Status` = fit_status,
      `R Squared` = r_squared
    )

  gt(regional_tbl) |>
    fmt_number(columns = c(`R Squared`), decimals = 3) |>
    fmt_missing(columns = everything(), missing_text = "-") |>
    tab_header(title = "Regional Curve Snapshot")
}
```
